Objectification in Action: SEM Supplement

### 2020-09-29 SEM analysis supplement/Final-Manuscript.tex
sem supplement cleaning

\documentclass[man]{apa6}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage{hyperref}
\hypersetup{unicode=true,
            pdftitle={Objectification in Action: Self- and Other-Objectification in Same-gender Interactions},
            pdfauthor={Randi L. Garcia, Kat Kyuchukova, Asha Hinson, \& Laneé Jung},
            pdfkeywords={keywords},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

@@

  \title{Objectification in Action: Self- and Other-Objectification in
Same-gender Interactions}
    \author{Randi L. Garcia\textsuperscript{1, 2}, Kat
Kyuchukova\textsuperscript{1, 2}, Asha Hinson\textsuperscript{1}, \&
Laneé Jung\textsuperscript{2}}
    \date{}

\shorttitle{Objectification in Action}
\affiliation{
\vspace{0.5cm}
\textsuperscript{1} Department of Psychology, Smith College\\\textsuperscript{2} Program in Statistical and Data Sciences, Smith College}
\keywords{keywords}
\usepackage{csquotes}
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

@@

Correspondence concerning this article should be addressed to Randi L.
Garcia, 415 Bass Hall, Smith College, Northampton, MA 01060. E-mail:
\href{mailto:rgarcia@smith.edu}{\nolinkurl{rgarcia@smith.edu}}}

\abstract{
Extant research on interpersonal objectification has focused mostly on
links between objectification, self-objectification, and negative
outcomes for women within mixed-gender interactions (Garcia, Earnshaw,
\& Quinn, 2016; Gervais, Sáez, Riemer, \& Klein, 2020). The purpose of
the present study was to extend past research on interpersonal
objectification to interactions between pairs of women. Women were
brought into the laboratory and interacted face-to-face in same-sex
dyads. Dyadic analysis (Kenny, Kashy, \& Cook, 2006) was utilized to
detect whether partners' objectification of each other affected state
self-objectification, as well as the resulting feelings of comfort and
authenticity during the interaction. Results revealed a significant
positive relationship between being objectified by a woman interaction
partner and women's own self-objectification (a partner effect). There
was no significant relationship between self-objectification and
interaction inauthenticity. Further, there were significant negative
effects of inauthenticity on career aspirations and relationship agency
(actor effects). The significant partner effect of objectification on
self-objectification suggests that women being objectified by other
women may result in feelings of self-objectification, and this finding
opens up questions for future research about how interpersonal
objectification might function in situations without an immediate male
gaze.

@@

Barbara L Fredrickson and Roberts (1997) Objectification Theory,
suggests that, in addition to being steeped in a culture that
objectifies women, women are objectified in actual interpersonal
encounters. The negative effects of this interpersonal objectification
for women are theorized be the strongest when it is a man doing the
objectifying (Calogero, 2004; Gay \& Castano, 2010; Gervais, Vescio, \&
Allen, 2011), but what are the consequences when a woman objectifies
another woman in an interaction? Psychological researchers studying the
sexual objectification of women, have in recent years explored the
interpersonal process of the objectification, finding evidence for
\emph{self}-objectification in the target as a proximal consequence of
being objectified (Garcia et al., 2016; Riemer, Sáez, Brock, \& Gervais,
2020; Strelan \& Pagoudis, 2018). In a recent review, Gervais et al.
(2020) organized the extant literature on interpersonal
self-objectification and proposed a theoretical model called the Social
Interaction Model of Objectification (SIMO). The SIMO is useful for
studying mixed-gender interactions, but what about interactions among
women? Although there is evidence that women objectify other women
(Loughnan et al., 2015a; Puvia \& Vaes, 2013), studies investigating the
process of interpersonal objectification in interactions between women
is scarce.

Is objectification by a female interaction partner related to an
increases in self-objectification for the woman being objectified?
Further, does objectification by a woman have the same downstream
negative consequences for women as being objectified by a male
interaction partner? The current study begins to address these questions
by investigating interpersonal objectification among interacting pairs
where both partners identify as women.

\subsection{Self-Objectification}\label{self-objectification}

Self-objectification is a psychological process that provides that
translates the experiences of interpersonal objectification {[}Loughnan
et al. (2015a); Gervais et al. (2020) into negative mental health
outcomes (e.g., interaction inauthenticity, anxiety, self-esteem, and
cognitive performance) (Calogero, Tantleff-Dunn, \& Thompson, 2011;
Moradi \& Huang, 2008). Calogero et al. (2011) proposes that
self-objectification can be conceptualized as a learned trait, or
\emph{trait} self-objectification (TSO), whereby one abopts a habitual
third-person perspective on one's own appearance. Furthermore,
self-objectification can also be elicited momentarily, for example, when
viewing sexualized images in movies and magazines (Morry \& Staska,
2001), when trying on sexualizing clothing (Barbara L Fredrickson,
Roberts, Noll, Quinn, \& Twenge, 1998), or during video chat when you
believe your interaction partner can only see your body (not face;
Saguy, Quinn, F Dovidio, \& Pratto, 2010). This momentary
self-objectification is referred to as \emph{state} self-objectification
(SSO; Bernard, Legrand, \& Klein, 2018; Calogero et al., 2011; Moradi \&
Huang, 2008) and is characterized by feeling like a body rather than a
full self within a particular moment, instance, or context.

There is evidence that being objectified by another person during an
interaction elicits SSO. For example, Loughnan, Baldissarri, Spaccatini,
and Elder (2017) found that for women, imagining a time when they were
objectified by another person cause reductions in human traits
attributed to the self, and further, the gender of the person doing the
objectification was not a moderating factor. In addition, in a
face-to-face mixed-gender dyadic study, Garcia et al. (2016) found that
men's reported objectification of their female interaction partner was
associated with increased self-objectification as reported by their
female partner. Further, this negative effect of the men's
objectification on women's SSO was strongest for women higher in TSO.
The current study uses this same dyadic paradigm to study same-gender,
woman-woman interacting pairs.

\subsection{Women Objectifying Women}\label{women-objectifying-women}

Past research investigating women objectifying other women has focused
on the psychological conditions that led women to objectify women.
Harsey and Zurbriggen (2020) found that self-objectification was related
to the objectification of women to a similar degree for male and female
participants. Along the same lines, Strelan and Hargreaves (2005) found
that the more women self-objectify, the more they objectify other women.
Could the process work in the other direction as well, that is, could
objectification by a woman produce self-objectification, in a similar
manner to objectification by a man? Hill and Fischer (2008) assessed
women's experiences of objectification from men independently from
women's experiences of objectification from other women. They found that
women may be socialized not only to see themselves as objects, but
perhaps to see other women as objects as well. This process, however,
was not comfirmed to occur during an actual interpersonal interaction.
Loughnan et al. (2015a) found that women objectify other women to a
greater extent than they objectify men. Women have also been found to
objectify (dehumanized) sexualized targets presented as images (Puvia \&
Vaes, 2013), but very little is known about interpersonal sexual
objectification among women and what the proximal effects of this
objectification might be. We do know that objectification has more
adverse consequences for women than men (Gervais et al., 2011; Moradi \&
Huang, 2008; Saguy et al., 2010), however, if women objectify other
women, perhaps even to a stronger degree than they objectify men, this
woman to woman objectification might have detrimental outcomes.

\subsection{Interpersonal
Objectification}\label{interpersonal-objectification}

Studies have shown that within social encounters women are gazed at more
than men (Briton \& Hall, 1995), often times feel \enquote{looked at}
within interpersonal interactions (Argyle \& Williams, 1969;
Miles-McLean et al., 2015), and are likely to internalize the
objectifying gaze on their physical self (Puvia \& Vaes, 2013; Young,
1979). Interpersonal objectification has been found to have negative
consequences for women. Gervais et al. (2011) found that an objectifying
gaze by a male interaction partner (confederate) was associated with
lower math performance for women, than being objectified by a female
interaction partner. Perhaps the most adverse negative consequence of
interpersonal objectificaiton is that being objectified socializes girls
and women to routinely treat themselves as objects to be looked at and
evaluated (Bartky, 1990; Berger, Cohen, \& Zelditch Jr, 1972; Barbara L
Fredrickson et al., 1998). Gervais et al. (2020) recently reviewed the
research on interpersonal objectification and organized our current
theoretical understanding of this process in the Social Interaction
Model of Objectification (SIMO). What is clear from Gervais et al.
(2020)'s review is that we know little about women-on-women
interpersonal objectification. Could there also be negative consequences
for women of interpersonal objectification by women?

Researchers have also studied interpersonal objectification and
self-objectification in romantic relationships (Strelan \& Pagoudis,
2018), in addition to interactions with strangers. Among heterosexual
male and female college students, self-objectification has been found to
be positively associated with the extent to which they objectify their
romantic partners (Zurbriggen, Ramsey, \& Jaworski, 2011). Evidence is
mixed, suggesting that women can sometimes have positive outcomes from
appearance valuation within the context of an established romantic
relationship. There is also evidence that they experience less SSO after
appearance comments within romantic relationships (Meltzer, 2020), but
less is known about first dates. An important caveat to this literature
is that it is only about heterosexual relationships. A recent study has
investigated the effect of self-objectification on the reduction of
relationship building skills in general (including same-sex friendships)
(Terán, Jiao, \& Aubrey, 2020). Both romantic relationships and stranger
encounters have been studied in the context of objectification, but
neither of these literatures have investigated specifically same-gender
relationships.

There is evidence that the experience of state self-objectification in
mixed-gender contexts (stranger and romantic) has negative consequences
for women, but what about in the context of interactions with other
women? Is the self-objectification experienced in mixed-gender
interactions associated with the same negative process as that
experienced in same-gender interactions? The ample research
demonstrating that the male gaze has a particularly detrimental effect
for women would suggest no (Calogero, 2004; Gay \& Castano, 2010;
Gervais et al., 2011; Saguy et al., 2010; Yilmaz \& Bozo, 2019), but,
there is evidence that women do objectify other women (Harsey \&
Zurbriggen, 2020; Loughnan et al., 2015a; Puvia \& Vaes, 2013) and to
would be helpful to understand the consequencs of this intragroup
objectification for women. When women objectify other women, does it
lead to self-objectification in the same way men's objectification of
women does (Garcia et al., 2016)? If so, does the self-objectification
experienced in these same-gender interactions have the same negative
consequences for authenticity in that interaction?

There is some evidence that reduced authenticity is a consequence of
self-objectification (Garcia et al., 2016; Terán et al., 2020). This
link has been justified by the literature on stigmatized-stigmatizer
interactions (M. R. Hebl \& Dovidio, 2005; Richeson \& Shelton, 2003;
Shelton, Richeson, \& Salvatore, 2005), viewing the experience of being
objectified in an interaction as an identity threat situation
(Miles-McLean et al., 2015; Nadal \& Haynes, 2012). Further, empirical
evidence reveals that objectification manifests through inauthenticity
in romantic relationships (Brunell et al., 2010), adverse attitudes in
regard to career aspirations, and a decrease in concentration and
impairment in female cognitive performance (Kahalon, Shnabel, \& Becker,
2018; D. M. Quinn, Chaudoir, \& Kallen, 2011). When a woman is
objectified by a man, and subsequently experiences self-objectification,
the intergroup nature of this encounter might trigger identity threat.
Thus, perhaps there are fewer negative consequences when a woman is
objectified by another woman, specifically, woman-woman interpersonal
objectification processes might diverge from mix-gender interpersonal
objectification processes precisely because they are not intergroup
interactions (at least with respect to gender identity). A woman
objectified by another woman may not be having the same negative
consequences that cascade from situations that trigger group-based
identity threat (Deaux \& Major, 1987; Dovidio, Hebl, Richeson, \&
Shelton, 2006; M. R. Hebl \& Dovidio, 2005), but feeling like a body,
rather than a full human, in any interaction (intergroup or ingroup) may
be enough to reduce women's feelings of authenticity and social
competence, regardless of the gender of the objectifyer (Terán et al.,
2020; Tolman, Impett, Tracy, \& Michael, 2006).

\subsection{The Current Study}\label{the-current-study}

In the current study, we sought to examine what occurs during an
interaction in which one or both partners are objectifying each other,
similarly to Garcia et al. (2016), but between same-gender interpersonal
interactions among women. Moreover, the current study uses a
face-to-face interaction paradigm and dyadic data analysis techniques to
examine the effects for both women simultaneously. Although the
literature on woman-woman objectification is small, the results are
mixed, and does not cover interpersonal encourters, we expected to
replicate some of the results found in Garcia et al. (2016). Most
importantly, we predicted that being objectified by one's interaction
partner would lead to self-objectification. We also expected that TSO
would moderate this relationship, amplifying the positive assocaition
between being objectified and SSO for women higher in TSO. Here we would
like to note that Puvia and Vaes (2013) would alternatively predict that
women's tendency to self-objectify (TSO) leads them to objectify other
women (more precisely, to dehumanize a sexualized woman). In addition,
Strelan and Hargreaves (2005) and Harsey and Zurbriggen (2020) would
predict the TSO to other-objectification link, further theorizing that
this relationships is mediated by the woman's own state
self-objectification (SSO). This limited, but extant, set of literature
on woman-woman objectification points to a possible alternative model
from the model hypothesized in the current study. Where appropriate, we
report results considering the causal directions implied by this
alternative mediation model.

We also tested whether SSO would, in turn, lead to feelings of
inauthenticity. The investigation of the SSO - inauthenticity connection
is considered exploratory given the lack of support for this connection
from the literature on identity threat in intragroup interactions
(Rollero, 2016) but support for this connection in the objectification
literature (Garcia et al., 2016; Terán et al., 2020). Regardless of
whether there was an association between SSO and inauthenticity, we
hypothesized that feelings of inauthencity would be associated with
reduced feelings of agency in romantic relationships, reduced career
aspiration, and reduced cognitive performance. In summary, we expected
to find a positive relationship between other-objectification by one's
partner and state self-objectification. We also expected to find a
negative relationship between self-state objectification and interaction
authenticity, and that interaction authenticity will be positively
related to cognitive performance, relationship agency, and career
aspirations.

@@

Except for the instructions given to participants, the procedure used
was identical to that in Garcia et al. (2016). In brief, that
methodology is that each participant arrived at the laboratory and were
then led into separate cubicles to prevent any communication between the
participants before the interaction. In addition, each participant was
screened for prior acquaintance to confirm that they had not met prior
to the study. They were asked to sign the consent form to participate,
and the study was described as follows: \enquote{This is a study looking
at how students form different types of relationships at college.} A
prompt on the computer screen told the participants that they were
assigned to the \enquote{College Relationships} condition and gave the
following instructions:

\begin{quote}
There are many types of relationships people form in college. During the
interaction, please think about your partner's potential as a romantic
partner. \textbf{Even if they are not the gender you are attracted to},
you can still judge their potential as a romantic partner. After the
interaction you will be asked to evaluate how dateable your partner is.
In other words, we would like to know if you think someone would date
your interaction partner. Also, your interaction partner will be
evaluating you in the same manner.
\end{quote}

\emph{All} participants were told that they were assigned to the
\enquote{College Relationships} condition. Self-objectification has been
found to occur after a mere relationship prime among women (Sanchez \&
Broccoli, 2008) because, in Westurn culture and beyond, women need to
look attractive to obtain and maintain successful relationship, thus,
the \enquote{College Relationships} condition may heighten
self-objectification and the evaluation of other women in a sexualized
way. The decision was made to ask even heterosexual women to judge their
fellow-woman partners for their potential as romantic partners. We felt
that this prompt would keep the study closest to a replication of the
previous Garcia et al. (2016) version of the study, and strengthen the
potential for objectification that would normally be low in the context
of a psychology laboratory. Recall that, past research has found that
heterosexual women are indeed able to evaluate other women's potential
as romantic partners (i.e., their sexual attractiveness; Puvia \& Vaes,
2013)---indeed, women may be unfortunately quite used to thinking about
their own \enquote{datability,} and we suspect this this habitual
thought pattern will translate to their thoughts about other women.

After recieving the \enquote{College Relationships} prompt, the two
participants were then brought into a larger interaction room where they
sat on stools prearranged to be approximately 1 meter apart. The
experimenter instructed the participants to \enquote{get to know each
other} for 10 minutes and then left the room. After 10 minutes, the
experimenter came back into the room and stopped the interaction. The
participants then went back to their individual cubicles and completed a
set of post-interaction measures. Participants were then thanked for
their participation and debriefed. More detail on this methodology can
be found in Garcia et al. (2016).

\subsection{Participants}\label{participants}

Thirty-two previously unacquainted dyads of self-identifying women
participated in this study. Data from two demographically similar higher
education institutions in the Northeast United States were combined to
create the final analysis sample (\emph{N =} 64) used in this study. In
the measures section that follows we refer to them as Sample 1 and
Sample 2. Sample 1 (\emph{N =} 24) is from a co-ed liberal arts college
and Sample 2 (\emph{N =} 40) is from a women's liberal arts college.
More specifically, twelve of the pairs were students at a co-ed liberal
arts college, while the remaining twenty pairs attended a women's
liberal arts college.\footnote{Initially, data was collected from both
  same-gender and mixed-gender dyads at both institutions. Sample 1
  originally consisted of 22 pairs, 12 men and 32 women. In Sample 2
  there were 23 pairs made up of 43 women and one man, as well as two
  participants who did not identify with either gender category. To
  investigate only same-gender pairs of women, we limited participant
  data to women in both samples.} All results presented below are from
models including sample as a control variable.

The participants were mostly first-year college students, with an
average age of 18.85 (SD = 1.04). The sample was 48.44\% White/European
American, 9.38\% Black/African-American, 28.12\% Asian/Pacific Islander,
9.38\% Latinx, and 4.69\% mixed-race. There were 8 White/White pairs and
4 same race racial minority pairs, for a total of 12 same-race pairs.
The remaining 20 were mixed race pairs, of which 15 were White/racial
minority pairings and 5 were cross-racial minority group pairs. 64.06\%
of the sample identified as heterosexual, and 25\% identified as gay,
lesbian or bisexual. See the analysis of differences between
heteroseuxal and non-heterosexual women in levels of
other-objectification of their female partners in the measures section
below.

@@

\begin{table}[tbp]
\begin{center}
\begin{threeparttable}
\caption{\label{tab:corrtable}Correlations and Descriptive Statistics among Study Variables}
\begin{tabular}{llllllllll}
\toprule
 & \multicolumn{1}{c}{$M$} & \multicolumn{1}{c}{$SD$} & \multicolumn{1}{c}{1.} & \multicolumn{1}{c}{2.} & \multicolumn{1}{c}{3.} & \multicolumn{1}{c}{4.} & \multicolumn{1}{c}{5.} & \multicolumn{1}{c}{6.} & \multicolumn{1}{c}{NA}\\
\midrule
1. Actor's trait self objectification (TSO) & -0.35 & 2.64 &  &  &  &  &  &  & \\
2. Actor's objectification of partner & -1.58 & 1.21 & .20 &  &  &  &  &  & \\
3. Partner's objectification of the actor & -1.58 & 1.21 & .09 & .14 &  &  &  &  & \\
4. Actor's state self-objectification & 1.92 & 1.13 & .13 & -.09 & .30* &  &  &  & \\
5. Actor's authenticity of interaction & 5.23 & 1.02 & -.02 & -.07 & .03 & -.10 &  &  & \\
6. Actor's future relationship agency & 4.69 & 0.96 & .04 & .09 & -.10 & -.09 & .23+ &  & \\
7. Actor's cognitive performance & 5.03 & 2.29 & .08 & .11 & .06 & .02 & .11 & .07 & \\
8. Actor's career aspirations & 3.88 & 0.61 & .05 & -.14 & -.08 & .01 & .33** & .26* & -.07\\
\bottomrule
\end{tabular}
\end{threeparttable}
\end{center}
\end{table}

The following measures were collected in the order they are presented
following the interaction. Correlations and descriptive statistics
appear in Table~\ref{tab:corrtable}.

@@

To measure the participant's objectification of their partner in the
interaction, participants were asked a series of questions about the
frequency of thoughts in relation to multiple characteristics of their
partner (Garcia et al., 2016). Questions included aspects of their
partner's internal traits such as personality, friends, family, and
extracurricular interests, as well as external traits such as body,
appearance, clothing, and body parts. All questions were rated on a
scale from 1 (not at all) to 7 (constantly). Objectification was
measured by taking the difference between the average frequency of
thought about their partner's external traits (\(\alpha\) = 0.79 for
Sample 1, \(\alpha\) = 0.79 for Sample 2) and frequency of thought about
their partner's internal traits (\(\alpha\) = 0.79 for Sample 1,
\(\alpha\) = 0.76 for Sample 2). A positive score in this scale would
indicate that the participant thought about their partner's external
traits more than the partner's internal traits, and a negative score
would indicate the opposite.

As can be seen in Table~\ref{tab:corrtable}, the mean
other-objectification of women by women was \emph{M =} -1.58 (\emph{SD
=} 1.21). This corresponds to women objectifying other women to a
\emph{greater} extent than women's objectification of men reported in
Garcia et al. (2016) (\emph{M =} -1.68, \emph{SD =} 1.52). Further, in
the current sample the difference in other-objectification between
heterosexual (\emph{M =} -1.77, \emph{SD =} 1.14) and non-heterosexual
women (\emph{M =} -1.39, \emph{SD =} 1.35) was not statistically
significant, \emph{t}(25.89) = 1.02, \emph{p =} 0.32.

@@

To assess state self-objectification, we used an average of two items
from Saguy et al. (2010) that were also used in Garcia et al. (2016).
Participants were asked to rank how much they agreed with the following
statements: \enquote{During the interaction I felt more like a body than
a full self} and \enquote{I felt more like a body than as a real person
in the interaction}. Originally, Saguy et al. (2010) used 3 items, but
in both samples the reliability of the scale was higher once the third
item was removed, so we chose to only use the first two for our measure
of SSO, leaving us with a reliable scale (\(\alpha\) = 0.84 for Sample
1, and \(\alpha\) = 0.85 for Sample 2.)

@@

>>>>

\documentclass[man]{apa6}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage{hyperref}
\hypersetup{unicode=true,
            pdftitle={Objectification in Action: SEM Supplement},
            pdfauthor={Kat Kyuchukova, Asha Hinson, \& Randi L. Garcia},
            pdfkeywords={keywords},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

@@

  \title{Objectification in Action: SEM Supplement}
    \author{Kat Kyuchukova\textsuperscript{1}, Asha Hinson\textsuperscript{1}, \&
Randi L. Garcia\textsuperscript{1}}
    \date{}

\shorttitle{SEM Supplement}
\affiliation{
\vspace{0.5cm}
\textsuperscript{1} Smith College}
\keywords{keywords}
\usepackage{csquotes}
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

@@

Correspondence concerning this article should be addressed to Kat
Kyuchukova, Postal address. E-mail:
\href{mailto:my@email.com}{\nolinkurl{my@email.com}}}

\abstract{
Objectification theory is a valuable framework for conceptualizing the
psychological consequences of being female within a society that
sexually objectifies the female body, and considering the ways in which
girls and women are acculturated to then internalize an observer's
perspective as a primary view of their appearance. Empirical evidence
has largely elucidated links between objectification,
self-objectification, and negative outcomes for woman within
interpersonal interactions between male-female pairs particularly. The
purpose of the present study was to extend past research and consider
the relationships between such valuable phenomena and their effects on
authenticity within interactions between female pairs. Woman were
brought into the laboratory and interacted in same-sex dyads. Dyadic
analysis was utilized to detect whether partners' objectification of
each other affected state self-objectification, and the resulting
feelings of comfort and authenticity during the interaction. After the
interaction, participants completed a questionnaire which measured many
constructs including cognitive performance, career aspirations, and
relationship agency. Results revealed no significant relationship
between self-objectification and authenticity. Further, although there
were significantly negative effects on career aspirations and
relationship agency resulting from a lack of relationship authenticity,
there was no evidence that this is due to feelings of sexual
objectification. The significant partner effect of objectification on
actor self-objectification suggests that women being objectified by
other women still results in feelings of self-objectification, and such
research has powerful implications for the ways that women interact in
both sexual and non-sexual settings.

@@

\section{Introduction}\label{introduction}

Theorists across diverse disciplines have explored the multiple ways
that the body conveys social meaning, as well as how these meanings
shape gendered experiences and therefore inform individuals' thinking,
feeling, and behavior, especially during interpersonal interactions with
members of different social groups (``Engendered lives,'' 1993).
Empirical evidence illustrates how women, in particular, continue to be
objects of perpetual discrimination as a result of psychosocial markers,
like gender, that produce modes through which their identity is
understood (Swim, Hyers, Cohen, \& Ferguson, 2001). Objectification
theory, a valuable theoretical framework proposed by Barbara L
Fredrickson and Roberts (1997) which works to contextualize female
bodies as socio-cultural constructions, can be employed to illuminate
the gender oppression and negative lived experiences of girls and women.
Additionally, one of the most detrimental forms of discrimination
against them is thought to be the process by which their whole being is
viewed as a collection of sexualized body parts valued predominantly for
commodification, a phenomena termed sexual objectification (Bartky,
1990). Sexual objectification occurs with both \enquote{endless variety
and monotonous similarity,} and is thus mediated by unique combinations
of race, ethnicity, sexuality, age, and class (Barbara L. Fredrickson,
Hendler, Nilsen, O'Barr, \& Roberts, 2011; Rubin, 1975, cited in Fraser
and Nicholson (1989), p.~28). Amid such heterogeneity though,
\enquote{having a reproductively mature female body} proposed by Barbara
L Fredrickson and Roberts (1997) is likely to create a shared
vulnerability to sexual objectification and a variety of shared negative
experiences as a result. Studies have shown that within social
encounters women are gazed at more than men (Briton \& Hall, 1995),
often times feel \enquote{looked at} within interpersonal interactions
(Argyle \& Williams, 1969), and will more than likely internalize the
objectifying gaze on physical self (Young, 1979). Moreover, perhaps the
most adverse effect of objectifying treatment is that it effectively
socializes girls and women to treat themselves as objects to be looked
at and evaluated, an effect termed self-objectification (Bartky, 1990;
Berger, Cohen, \& Zelditch Jr, 1972; Barbara L Fredrickson, Roberts,
Noll, Quinn, \& Twenge, 1998). Self-objectification is a
multidimensional process that accounts for the cognitive mechanism that
translates experiences of sexualization at the cultural level to
psychological (e.g., anxiety, self-esteem, authenticity, motivational
states) and behavioral (cognitive performance, body monitoring) features
of mental health and well-being at the individual level (Calogero,
Tantleff-Dunn, \& Thompson, 2011; Moradi \& Huang, 2008). Calogero et
al. (2011) proposes that the construct of self-objectification can be
conceptualized as a learned trait. Furthermore, it can also be elicited
momentarily, through the media, for example, with sexualized images in
movies and magazines, which can lead to a state of self-objectification
(Calogero et al., 2011, Moradi and Huang (2008)). Being objectified by
another person and possessing trait-level self-objectification (TSO) may
interact to influence experiences of feeling like a body, or state
self-objectification (SSO). In the current work, we sought to examine
what occurs during an interaction in which one or both partners are
objectifying each other, similarly to Garcia, Earnshaw, and Quinn
(2016), but between same-sex female interpersonal interactions. We
predicted that being objectified by one's interaction partner would lead
to self-objectification, in addition to modified feelings of
authenticity in postinteraciton outcomes, including feelings of agency
in romantic relationships, career aspiration, and cognitive performance
(D. M. Quinn, Chaudoir, \& Kallen, 2011). Empirical evidence reveals
that objectification manifests through inauthenticity in romantic
relationships (Brunell et al., 2010), adverse attitudes in regard to
career aspirations, and a decrease in concentration and impairment in
female cognitive performance (Swim et al., 2001). Moreover, it was the
goal of this research to empirically explore the role of interaction
authenticity in objectification by utilizing a structural equation
modeling to examine the effects for both women simultaneously. We
expected to replicate the results found in the previous Garcia et al.
(2016) study. More specifically, we expected to find a positive
relationship between state-other objectification and self-state
objectification, and a resulting negative relationship between
self-state objectification and interaction authenticity. Finally, we
expected there to be a positive relationship between interaction
authenticity and cognitive performance, relationship agency, and career
aspirations.

@@

The procedure used was identical to that in Garcia et al. (2016), except
for the instructions that the participants were given. In brief, that
methodology is that each participant arrived at the laboratory and were
then led into separate cubicles to prevent any communication between the
participants before the interaction. In addition, each participant was
screened for prior acquaintance to confirm that they had not met prior
to the study. They were asked to sign the consent form to participate,
and the study was described as follows: \enquote{This is a study looking
at how students form different types of relationships at college.} A
prompt on the computer screen told the participants that they were
assigned to the \enquote{College Relationships} condition and gave the
following instructions:

There are many types of relationships people form in college. During the
interaction, please think about your partner's potential as a romantic
partner. Even if they are not the gender you are attracted to, you can
still judge their potential as a romantic partner. After the interaction
you will be asked to evaluate how dateable your partner is. In other
words, we would like to know if you think someone would date your
interaction partner. Also, your interaction partner will be evaluating
you in the same manner.

Two participants were then brought into a larger interaction room where
they sat on stools prearranged to be 36 inches apart. The experimenter
instructed the participants to \enquote{get to know each other} for 10
minutes and then left the room. After 10 minutes, the experimenter came
back into the room and stopped the interaction. The participants then
went back to their individual cubicles and completed a set of
post-interaction measures. Participants were then thanked for their
participation and debriefed Garcia et al. (2016). The full methodology
used is found in Garcia et al. (2016)'s study.

\subsection{Combining Samples}\label{combining-samples}

Data from two different samples were used for this study and are
discussed below. In the measures section that follows we refer to them
as Sample 1 and Sample 2. Sample 1 is from a co-ed liberal arts college
in the northeast and Sample 2 is from a women's liberal arts college in
the northeast.

@@

The following measures were collected in the order they are presented
following the interaction. Correlations appear in
Table~\ref{tab:corrtable}, and descriptive statistics appear in
Table~\ref{tab:descriptives}.

@@

To measure the participant's objectification of their partner in the
interaction, participants were asked a series of questions about the
frequency of thoughts in relation to multiple characteristics of their
partner Garcia et al. (2016). Questions included aspects of their
partner's internal traits such as personality, friends, family, and
extracurricular interests, as well as external traits such as body,
appearance, clothing, and body parts. All questions were to be rated on
a scale from 1 (not at all) to 7 (constantly). Objectification was
measured by getting the difference between the average frequency of
thought about their partner's external traits (\(\alpha\) = 0.79 for
Sample 1, \(\alpha\) = 0.79 for Sample 2) and frequency of thought about
their partner's internal traits (\(\alpha\) = 0.79 for Sample 1,
\(\alpha\) = 0.76 for Sample 2). A positive score in this scale would
indicate that the participant thought about their partner's external
traits more than the partner's internal traits, and a negative score
would indicate the opposite.

@@

To assess state self-objectification, we used an average of two items
from Saguy, Quinn, F Dovidio, and Pratto (2010) that were also used in
Garcia et al. (2016). Participants were asked to rank how much they
agreed with the following statements: \enquote{During the interaction I
felt more like a body than a full self} and \enquote{I felt more like a
body than as a real person in the interaction}. Originally, Saguy et al.
(2010) used 3 items, but in both samples the reliability of the scale
was higher once the third item was removed, so we chose to only use the
first two for our measure of SSO, leaving us with a reliable scale
(\(\alpha\) = 0.84 for Sample 1, and \(\alpha\) = 0.85 for Sample 2.)

@@

\begin{verbatim}
## [1] "R [Version 3.5.2; @R-base]"
\end{verbatim}
